Precise Asymptotics of Transferring from Different Regression in High Dimensions

### 2021-06-12 revision_journal/main_arxiv.tex
revision wip

\def\shownotes{0}
\usepackage{natbib}
\setcitestyle{authoryear,open={(},close={)}}
\renewcommand{\cite}{\citep}
\usepackage[export]{adjustbox}
\usepackage[margin=1in]{geometry}
\usepackage{subfloat}
\usepackage[T1]{fontenc}    %
\usepackage{nicefrac}       %
\usepackage{microtype}      %
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{macro_math}
\usepackage{macro_fan}
\usepackage{stmaryrd}
\usepackage{multirow}
\usepackage[us,12hr]{datetime}
\usepackage[utf8]{inputenc} %
\usepackage{caption,subcaption}

\usepackage{dsfont}

\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}

\usepackage{authblk}

@@

\title{\textbf{Sharp Bias-variance Tradeoffs of Hard Parameter Sharing in High-dimensional Linear Regression}}
\vspace{0.15in}
\author[1]{Hongyang R. Zhang\thanks{HZ and FY contributed equally to the theoretical results. SW conducted the experimental analysis. Correspondence to hrzhang@northeastern.edu or fyang75@wharton.upenn.edu.}}
\author[2]{Fan Yang\samethanks}
\author[3]{Sen Wu\samethanks}
\author[2]{Weijie J. Su}
\author[3]{Christopher R\'e}
\vspace{0.15in}
\affil[1]{Khoury College of Computer Sciences, Northeastern University}
\affil[2]{Department of Statistics, The Wharton School, University of Pennsylvania}
\affil[3]{Department of Computer Science, Stanford University}

\maketitle

\input{intro}
\input{setup}
\input{same_cov}
\input{diff_cov}
\input{experiments}
\input{experiments_text}
\input{conclusions}

\subsection*{Acknowledgements:}
Thanks to Edgar Dobriban, Vaggos Chatziafratis, Mayee Chen, and Ruoxuan Xiong for helpful discussions at various stages of this work.
HZ and WS's contributions were in part supported by the Wharton Dean's Fund for Postdoctoral Research.
We gratefully acknowledge the support of DARPA under Nos. FA86501827865 (SDH) and FA86501827882 (ASED); NIH under No. U54EB020405 (Mobilize), NSF under Nos. CCF1763315 (Beyond Sparsity), CCF1563078 (Volume to Velocity), and 1937301 (RTML); ONR under No. N000141712266 (Unifying Weak Supervision); the Moore Foundation, NXP, Xilinx, LETI-CEA, Intel, IBM, Microsoft, NEC, Toshiba, TSMC, ARM, Hitachi, BASF, Accenture, Ericsson, Qualcomm, Analog Devices, the Okawa Foundation, American Family Insurance, Google Cloud, Swiss Re, the HAI-AWS Cloud Credits for Research program, and members of the Stanford DAWN project: Teradata, Facebook, Google, Ant Financial, NEC, VMWare, and Infosys. The U.S. Government is authorized to reproduce and distribute reprints for Governmental purposes notwithstanding any copyright notation thereon. Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views, policies, or endorsements, either expressed or implied, of DARPA, NIH, ONR, or the U.S. Government.

\bibliographystyle{plainnat}
\bibliography{rf,ref_mtl}
\appendix

\input{proof_same_cov}
\input{proof_gaussian_case}
\input{proof_appd}
\input{proof_examples}
\input{tools}
\end{document}

>>>>

\def\shownotes{1}

\usepackage{natbib}
\setcitestyle{authoryear,open={(},close={)}}
\renewcommand{\cite}{\citep}
\newcommand{\yell}[1]{{\color{red}#1}}
\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
\usepackage{authblk}
\usepackage[margin=1in]{geometry}
%\usepackage{hyperref}

\usepackage{macro_math}
\usepackage[us,12hr]{datetime} % `us' makes \today behave as usual in TeX/LaTeX
\usepackage{graphicx, subcaption}
\usepackage[export]{adjustbox}
\usepackage{subfloat}
\usepackage[T1]{fontenc}    %
\usepackage{nicefrac}       %
\usepackage{microtype}      %
\usepackage[hidelinks]{hyperref}
\hypersetup{colorlinks,linkcolor={blue},citecolor={blue},urlcolor={red}}
\usepackage{macro_fan}
\usepackage{stmaryrd}
\usepackage[utf8]{inputenc} %
\usepackage{caption,subcaption}

%\newcommand{\citet}{\cite}

@@

	\iffalse
	\vspace{0.15in}
	\author[1]{Hongyang R. Zhang\thanks{HZ and FY contributed equally to the theoretical results. SW conducted the experimental analysis. Correspondence to hrzhang@northeastern.edu or fyang75@wharton.upenn.edu.}}
	\author[2]{Fan Yang\samethanks}
	\author[3]{Sen Wu\samethanks}
	\author[2]{Weijie J. Su}
	\author[3]{Christopher R\'e}
	\vspace{0.15in}
	\affil[1]{Khoury College of Computer Sciences, Northeastern University}
	\affil[2]{Department of Statistics, The Wharton School, University of Pennsylvania}
	\affil[3]{Department of Computer Science, Stanford University}
	\fi
	\title{Precise Asymptotics of Transferring from Different Regression in High Dimensions}
	\maketitle
	\input{abstract}
	\input{intro}
	\input{results}
	\input{examples}
	\input{multitask}
	\input{exp}
	\input{conclusions}
	\bibliographystyle{plainnat}
	\bibliography{rf,ref_mtl}

\end{document}
